On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-08-22 Manuscript/manuscript.tex
Started to go through pooled revisions

\begin{figure}[tbp]
  \centering
  \includegraphics{Pooled_Boxplot}
  \caption{The reaction times from 1999 to 2022 for the men's final (top) and
  the men's semifinals and finals (bottom).}
  \label{fig:Boxplots}
\end{figure}

@@

For analysis purposes, we will often pool reaction times of men's final and 
men's semifinal heats together and refer to this data as the ``pooled data"
throughout the paper. 
%\of{Ok I updated this.  Should I delete the batch variable too?  Although I don't
%use it, I do reference it in the methods section}
The pooled data increases the sample size which is advantageous because in some
years there are very few final heat observations.  For example, in 2022 there
were only five data points due to two disqualifications and one athlete who 
did not compete.  We also look at data that does not include 2022 with year values
between 1999 and 2019.  Thus, we have four datasets with their respective naming
\jy{Clean up}
in parentheses: the final's data from 1999 to 2019 (Old Finals), final's data 
from 2019 to 2022 (All Finals), pooled data from 1999 to 2019 (Old Pooled), and 
pooled data from 1999 to 2022 (All Pooled).

The data under consideration is best visualized using side-by-side boxplots, as
shown in Figure~\ref{fig:Boxplots}.  It is clear that the reaction times in the 
2022 boxplot for both 
the men's finals and men's pooled semifinal and final data are lower (indicating 
faster reaction times)
than in previous years.  The median for the men's pooled data in 2022 was 0.129
and the median for the men's final data in 2022 was 0.126.  For comparison,
{brosnan2017effects} found median reaction times of 0.156 seconds 
for men when looking at data from 1999 to 2014.
We can also see from Figure~\ref{fig:Boxplots} that the reaction times clearly
differ from year to year. The venue of the World Championships changes each 
year, so weather or climate related factors such as humidity, precipitation, 
elevation, may indeed play a role, but additionally, both the technology and 
false start penalization rules have changed over the study period.

@@

\begin{table}
  \centering
  \caption{Summary statistics for the two effect GLMM on various data sets. SE
  is short for standard error.} 
  \begin{tabular}{c c c c c c}
      \toprule
      Dataset & AIC & Batch SE & Year SE & Intercept & Residual SE \\
      \midrule
      Old Pooled & 0.060 & 0.034 & $-1.865$ & 0.139 \\
      All Pooled & 0.059 & 0.041 & $-1.880$ & 0.014 \\
      \bottomrule
  \end{tabular}
  \label{tab:Gamma_parameters}
\end{table}

>>>>

@@

For analysis purposes, we will often pool reaction times of men's final and 
men's semifinal heats together which increases the sample size which is 
advantageous because in some years there are very few finals observations, such
as in 2022 there were only five data points due to two disqualifications and one
athlete who did not compete.  We also look at data can also look at data that
excludes 2022 to see how our analysis differs based on the exclusion of one
particular year of interest.

The data under consideration is best visualized using using a boxplots, as
shown in Figure~\ref{fig:Boxplot}.  It is clear that the reaction times in the 
2022 boxplot for both 
the men's finals and men's pooled semifinal and final data are lower (indicating 
faster reaction times)
than in previous years.  The median for the men's pooled data in 2022 was 0.129
and the median for the men's final data in 2022 was 0.126.  For comparison,
{brosnan2017effects} found median reaction times of 0.156 seconds 
for men when looking at data from 1999 to 2014.
We can also see from Figure~\ref{fig:Boxplots} that the reaction times clearly
differ from year to year. The venue of the World Championships changes each 
year, so weather or climate related factors such as humidity, precipitation, 
elevation, may indeed play a role, but additionally, both the technology and 
false start penalization rules have changed over the study period.

\begin{figure}[tbp]
  \centering
  \includegraphics{Boxplot}
  \caption{The reaction times from 1999 to 2022 for the men's final (top) and
  the men's semifinals and finals (bottom).}
  \label{fig:Boxplot}
\end{figure}

@@

\begin{table}
  \centering
  \caption{Summary statistics for the two effect GLMM on various data sets. SE
  is short for standard error.} 
  \begin{tabular}{c c c c c c}
      \toprule
      Dataset & AIC & $\sigma_h^2$ & $\sigma_v^2$ & $\alpha$ & $\delta_{i/j}$ \\
      \midrule
      Old Pooled & 0.060 & 0.034 & $-1.865$ & 0.139 \\
      All Pooled & 0.059 & 0.041 & $-1.880$ & 0.014 \\
      \bottomrule
  \end{tabular}
  \label{tab:Gamma_parameters}
\end{table}
